Forecasting the 2024 U.S. Presidential Election: Analyzing Poll Quality, Sample Size, and Regional Variations

### 2024-11-04 paper/paper.qmd
Fixed typos

We start by describing the dataset in detail and discussing key variables in the Data section (see [Data](#data)), where we present summary statistics and visualizations to better understand the data. The Model section (see [Model](#model)) introduces the Generalized Linear Model (GLM). This includes an exaplanation of the mathematical framework, assumptions, and variable selection process. We then detail the Results (see [Results](#results)), where we highlight key findings on how poll characteristics and state-level differences impact election forecasts. Finally, the Discussion (see [Discussion](#discussion)) addresses the implications of our findings, the limitations of our approach, and suggestions for future research. In the last part of the paper, we critique the method itself and attempt to abstract some of the learnings into our understanding of the world.

@@

The logistic regression model used has the following underyling assumptions:

@@

Since the sample is not drawn randomly, there are concerns over the degree of representativeness for the population. Non-random samples may over-represent certain groups, specifically in thie case internet-savvy individuals or those more engaged in politics have a higher likelihood of responding. The addition of post-stratification weighting helps balance the sample, however the accuracy of the results depends heavily on how well the quotas and weights align with the population. If the quotas are off, the results can be skewed (Baker et al., 2013; Pew Research Center, 2020).

@@

Non-response occurs when certain groups are less likely to respond to surveys, which can introduce **non-response bias**. To address this, YouGov uses **weighting**. After collecting responses, statistical weightsare applied to ensure that the final sample reflects the population’s demographic makeup to a high degree[@yougov2021].

@@

- **MTurk**, **Prolific**, and **YouGov** panels to access diverse respondents.Studies show that online recruitment platforms may produce quality survey data when sampling and weighting are done properly [@huff2015].

@@

### Sections:
1. **Screening Questions**:
   - U.S. citizenship and voter registration status.
   - Intention to vote.
2. **Demographics**:
   - Questions cover **age, gender, race/ethnicity, education, income level, and region**.
3. **Voting Intentions**:
   - “If the election were held today, who would you vote for?”
     - **Kamala Harris** (Democratic)
     - **Donald Trump** (Republican)
     - **Undecided**
   - Likelihood of voting rated on a **scale of 1-10**.
4. **Issues Important to Voting**:
   - Key issues (e.g., **Economy, Healthcare, Immigration, Climate Change**), ranked on a **scale of 1-5**.
5. **Candidate Favorability**:
   - Favorability ratings for **Kamala Harris** and **Donald Trump**, rated on a **5-point scale**.
6. **Political Engagement**:
   - This section will include questions on how closely respondents follow election news.
7. **Open-ended Questions**:
   - We end by asking open-ended questions around What factors the repsondents think most influence the voting decision?

@@

The survey includes **attention-check questions** and tracks **response time** to flag low-quality responses. In ordet to reduce noise due to bots filling these up quickly, responses completed in less than **3 minutes** will be excluded.

>>>>

We start by describing the dataset in detail and discussing key variables in the Data section (see [Data](#data)), where we present summary statistics and visualizations to better understand the data. The Model section (see [Model](#model)) introduces the Generalized Linear Model (GLM). This includes an explanation of the mathematical framework, assumptions, and variable selection process. We then detail the Results (see [Results](#results)), where we highlight key findings on how poll characteristics and state-level differences impact election forecasts. Finally, the Discussion (see [Discussion](#discussion)) addresses the implications of our findings, the limitations of our approach, and suggestions for future research. In the last part of the paper, we critique the method itself and attempt to abstract some of the learnings into our understanding of the world.

@@

The logistic regression model used has the following underlying assumptions:

@@

Since the sample is not drawn randomly, there are concerns over the degree of representativeness for the population. Non-random samples may over-represent certain groups, specifically in this case internet-savvy individuals or those more engaged in politics have a higher likelihood of responding. The addition of post-stratification weighting helps balance the sample, however the accuracy of the results depends heavily on how well the quotas and weights align with the population. If the quotas are off, the results can be skewed (Baker et al., 2013; Pew Research Center, 2020).

@@

Non-response occurs when certain groups are less likely to respond to surveys, which can introduce **non-response bias**. To address this, YouGov uses **weighting**. After collecting responses, statistical weights are applied to ensure that the final sample reflects the population’s demographic makeup to a high degree[@yougov2021].

@@

- **MTurk**, **Prolific**, and **YouGov** panels to access diverse respondents. Studies show that online recruitment platforms may produce quality survey data when sampling and weighting are done properly [@huff2015].

@@

### Sections:
1. **Screening Questions**:
   - U.S. citizenship and voter registration status.
   - Intention to vote.
2. **Demographics**:
   - Questions cover **age, gender, race/ethnicity, education, income level, and region**.
3. **Voting Intentions**:
   - “If the election were held today, who would you vote for?”
     - **Kamala Harris** (Democratic)
     - **Donald Trump** (Republican)
     - **Undecided**
   - Likelihood of voting rated on a **scale of 1-10**.
4. **Issues Important to Voting**:
   - Key issues (e.g., **Economy, Healthcare, Immigration, Climate Change**), ranked on a **scale of 1-5**.
5. **Candidate Favorability**:
   - Favorability ratings for **Kamala Harris** and **Donald Trump**, rated on a **5-point scale**.
6. **Political Engagement**:
   - This section will include questions on how closely respondents follow election news.
7. **Open-ended Questions**:
   - We end by asking open-ended questions around What factors the respondents think most influence the voting decision?

@@

The survey includes **attention-check questions** and tracks **response time** to flag low-quality responses. In order to reduce noise due to bots filling these up quickly, responses completed in less than **3 minutes** will be excluded.
